### 2024-07-19 evaluating-prediction-accuracy.qmd
20240719 - clean up
20240719 - links and formatting

$$
\begin{aligned}
  \text{root mean squared log error (RMSLE)} &= \sqrt{\sum\limits_{i = 1}^n log\bigg(\frac{\text{predicted}_i + 1}{\text{observed}_i + 1}\bigg)^2} \\
  &= \sqrt{\text{mean}\Bigg[log\bigg(\frac{\text{predicted}_i + 1}{\text{observed}_i + 1}\bigg)^2\Bigg]} \\
  &= \sqrt{\text{mean}\big[log(\text{accuracy ratio})^2\big]} = \sqrt{\text{mean}\Big\{\big[log(\text{predicted}_i + 1) - log(\text{actual}_i + 1)\big]^2\Big\}}
\end{aligned}
$$ {#eq-rootMeanSquaredLogError}

@@

Predictive $R^2$ is described here: https://tomhopper.me/2014/05/16/can-we-do-better-than-r-squared/ (archived at https://perma.cc/BK8J-HFUK).
Predictive $R^2$ penalizes [overfitting](#sec-overfitting), unlike traditional $R^2$.
Larger values indicate greater accuracy.

@@

The effect size of a predictor, i.e., the standardized regression coefficient is called a beta ($\beta$) coefficient, is a general index of [discrimination accuracy](#sec-discrimination) for a continuous outcome.
Larger values reflect greater accuracy.
We can obtain standardized regression coefficients by standardizing the predictors and outcome using the `scale()` function in R.

@@

```{r}
#| include: false

# Test reading file from the repo that was saved from another chapter
test <- read.csv(
  file = "./data/test.txt"
)
```

```{r}
#| echo: false

print(test)
```

>>>>

$$
\scriptsize
\begin{aligned}
  \text{root mean squared log error (RMSLE)} &= \sqrt{\sum\limits_{i = 1}^n log\bigg(\frac{\text{predicted}_i + 1}{\text{observed}_i + 1}\bigg)^2} \\
  &= \sqrt{\text{mean}\Bigg[log\bigg(\frac{\text{predicted}_i + 1}{\text{observed}_i + 1}\bigg)^2\Bigg]} \\
  &= \sqrt{\text{mean}\big[log(\text{accuracy ratio})^2\big]} = \sqrt{\text{mean}\Big\{\big[log(\text{predicted}_i + 1) - log(\text{actual}_i + 1)\big]^2\Big\}}
\end{aligned}
$$ {#eq-rootMeanSquaredLogError}

@@

Predictive $R^2$ is described here: <https://tomhopper.me/2014/05/16/can-we-do-better-than-r-squared/> (archived at <https://perma.cc/BK8J-HFUK>).
Predictive $R^2$ penalizes [overfitting](#sec-overfitting), unlike traditional $R^2$.
Larger values indicate greater accuracy.

@@

The effect size of a predictor, i.e., the standardized regression coefficient is called a beta ($\beta$) coefficient, is a general index of [discrimination accuracy](#sec-discrimination) for a continuous outcome.
Larger values reflect greater accuracy.
We can obtain standardized regression coefficients by standardizing the predictors and outcome using the `scale()` function in `R`.

@@
